### 2016-12-09 local-capability-machine.tex
indentation g1
indentation

                      \item Notice: $W = \revokeTemp(W)$

@@

              \begin{proof}[Proof of Lemma~\ref{lem:correctness-f3}]
                This proof goes like the proof of Lemma~\ref{lem:correctness-f3} except for item \ref{f2:c-prp}
                \begin{enumproof}[start=3]
                \item $\npair{\reg_0\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''}} \in \stdrr(W)$ \\
                  $\dots$
                  \begin{enumproof}[start=3]
                  \item $\npair{c_{\var{prp}}} \in \stdvr(W)$ \\
                    To this end let $n' < n$ and $W' \futurewk W$ be given and show
                    \[
                      \npair[n']{\updatePcPerm(c_\prp)} \in \stder(W')
                    \]
                    to this end let 
                    \begin{enumproof}
                    \item $n'' \leq n'$
                    \item $\npair[n'']{\reg} \in \stdrr(W')$
                    \item $\heapSat[\ms]{n''}{W'}$ \label{f3:mem-sat-mid}
                    \end{enumproof}
                    be given and show
                    \[
                      \npair[n'']{(\reg\update{\pcreg}{\updatePcPerm(c_\prp)},\ms)}
                    \]
                    to this end let $i \leq n''$, $\ms_f$, and $m''$ be given and assume
                    \begin{enumproof}[resume]
                    \item $(\reg\update{\pcreg}{c_\prp},\ms \uplus \ms_f) \step[i] (\halted,m'')$ \label{f3:mid-exec}
                    \end{enumproof}
                    now show

@@

>>>>

                      \item Notice: $W = \revokeTemp{W}$

@@

\begin{proof}[Proof of Lemma~\ref{lem:correctness-f3}]
  This proof goes like the proof of Lemma~\ref{lem:correctness-f3} except for item \ref{f2:c-prp}
  \begin{enumproof}[start=3]
  \item $\npair{\reg_0\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''}} \in \stdrr(W)$ \\
    $\dots$
    \begin{enumproof}[start=3]
    \item $\npair{c_{\var{prp}}} \in \stdvr(W)$ \\
      To this end let $n' < n$ and $W' \futurewk W$ be given and show
      \[
        \npair[n']{\updatePcPerm{c_\prp}} \in \stder(W')
      \]
      to this end let 
      \begin{enumproof}
      \item $n'' \leq n'$
      \item $\npair[n'']{\reg} \in \stdrr(W')$
      \item $\heapSat[\ms]{n''}{W'}$ \label{f3:mem-sat-mid}
      \end{enumproof}
      be given and show
      \[
        \npair[n'']{(\reg\update{\pcreg}{\updatePcPerm{c_\prp}},\ms)} \in \observations(W')
      \]
      to this end let $i \leq n''$, $\ms_f$, and $m''$ be given and assume
      \begin{enumproof}[resume]
      \item $(\reg\update{\pcreg}{c_\prp},\ms \uplus \ms_f) \step[i] (\halted,m'')$ \label{f3:mid-exec}
      \end{enumproof}
      now show

@@

\begin{lemma}
  Say the instructions for \texttt{scall} $r([r_{j_1},\dots,r_{j_n}],[r_{k_1},\dots, r_{k_m}])$ are $i_0,\dots,i_l$, then
  \begin{align*}
    & m = \ms \uplus \ms_\stk \uplus \ms_f \\
    & \memSat{\ms \uplus \ms_\stk}{W}
    & \npair{\reg[\pc \mapsto c_{\var{scall}}][r_\stk \mapsto c_\stk]} \in \stdrr(W) \\
    & \ms_\stk = m | _{\start_\stk,\addrend_\stk} \\
    & c_\stk = ((\rwlx,\gl),\start_\stk,\addrend_\stk,\addr) \\
    & \start_\stk-1 \leq \addr \land \start_\stk \leq \addrend_\stk \land \addr \leq \addrend_\stk \\
    & c_{\var{scall}} = ((\perm,\gl)\start,\addrend,\addr) \\
    & \perm \in \{\exec, \rwx, \rwlx\} \\
    & \addrend - \addr \leq l  \\
    & \ms(\addr) = i_0, \dots, \ms(\addr+l) = \mathtt{jmp r}
    & (\reg[\pc \mapsto c_{\var{scall}}][r_\stk \mapsto c_\stk],m) \step[i'] (\reg_0[r_{k_1} \mapsto \reg(r_{k_1})]\dots[r_{k_m} \mapsto \reg(r_{k_m})][\pc \mapsto c_{\var{scall}}'][r_\stk \mapsto c_\stk'],m) \\
    & c_{\var{scall}}'.\mathrm{a} = \addr+l \\
    & \quad \Rightarrow \\
    & \qquad \exists \ms_\stk', \ms', \ms_r \ldotp \\
    & \qquad \quad W' = \revokeTemp{W}[\var{rn}_1\mapsto\iota^\sta(\temp, )][\var{rn}_2 \mapsto \iota^\pwl] \\
    & \qquad \quad \memSat[n-i']{\ms_\stk'\uplus \ms'}{W'}
  \end{align*}
\end{lemma}
